\sysfull

### 2018-08-05 paper/asplos19/implementation.tex
remove COALA

%\texttt{COALA\_TASK} is a function annotation that declares a function to be a
%task. \texttt{COALA\_NEXT\_TASK}, indicates the task to run next, after an
%executing task completes.  \texttt{COALA\_PV} declare a new protected variable.
%The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
%respectively.  \texttt{COALA\_SM} identifies protected \texttt{struct} fields
%and tells \sys to ensure that the struct fields are page-aligned in memory.
%The programmer is required to explicitly call two API functions at the start of
%{\tt main()}: \texttt{COALA\_INIT}, which does global initialization upon first
%boot and \texttt{COALA\_RUN} which hands the control to \sys's task manager to
%resume task execution.

@@

\noindent\textbf{New Tasks.} The \texttt{COALA\_TASK} annotation on a function
declaration statically allocates a non-volatile constant variable holding a
task's weight and declares that the function is a task.\\
%
\noindent\textbf{Task Transitions.} A call to \texttt{COALA\_NEXT\_TASK} marks the task to be executed at the 
end of the current one task and it can be invoked along
any control path to dynamically determine the next task.\\
%
\noindent\textbf{Protected Variables.} The \texttt{COALA\_PV} annotation on a
variable statically allocates a protected non-volatile variable. The
variable must then be accessed with the \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.\\
%
\noindent\textbf{Initialization.} The behavior of the API method
\texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the
addition of performing preliminary kernel initializations, including hardware setup.\\
%
\noindent\textbf{Execution.} The programmer passes control to \sys's task scheduler 
by calling \texttt{COALA\_RUN} after device initialization. 
%
First the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks.

@@

 \textbf{Partial Commit and Task Atomicity.} Some applications prevent
downscaling a task because of a need for task atomicity.  For example, sampling
an analog signal requires consecutive samples at a known interval, or the
digitally sampled signal is meaningless.  In such a case, the programmer can
disable partial commit for a task or a span of code, marking  the code with a
pair of \texttt{COALA\_DISABLE\_PE} and \texttt{COALA\_ENABLE\_PE} annotations.
These annotations respectively halt and resume the partial execution timer.

>>>>

%\texttt{TASK} is a function annotation that declares a function to be a
%task. \texttt{NEXT\_TASK}, indicates the task to run next, after an
%executing task completes.  \texttt{PV} declare a new protected variable.
%The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
%respectively.  \texttt{SM} identifies protected \texttt{struct} fields
%and tells \sys to ensure that the struct fields are page-aligned in memory.
%The programmer is required to explicitly call two API functions at the start of
%{\tt main()}: \texttt{INIT}, which does global initialization upon first
%boot and \texttt{RUN} which hands the control to \sys's task manager to
%resume task execution.

@@

\noindent\textbf{New Tasks.} The \texttt{TASK} annotation on a function
declaration statically allocates a non-volatile constant variable holding a
task's weight and declares that the function is a task.\\
%
\noindent\textbf{Task Transitions.} A call to \texttt{NEXT\_TASK} marks the task to be executed at the 
end of the current one task and it can be invoked along
any control path to dynamically determine the next task.\\
%
\noindent\textbf{Protected Variables.} The \texttt{PV} annotation on a
variable statically allocates a protected non-volatile variable. The
variable must then be accessed with the \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.\\
%
\noindent\textbf{Initialization.} The behavior of the API method
\texttt{INIT} is very similar to \texttt{NEXT\_TASK}, with the
addition of performing preliminary kernel initializations, including hardware setup.\\
%
\noindent\textbf{Execution.} The programmer passes control to \sys's task scheduler 
by calling \texttt{RUN} after device initialization. 
%
First the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks.

@@

 \textbf{Partial Commit and Task Atomicity.} Some applications prevent
downscaling a task because of a need for task atomicity.  For example, sampling
an analog signal requires consecutive samples at a known interval, or the
digitally sampled signal is meaningless.  In such a case, the programmer can
disable partial commit for a task or a span of code, marking  the code with a
pair of \texttt{DISABLE\_PE} and \texttt{ENABLE\_PE} annotations.
These annotations respectively halt and resume the partial execution timer.
